---
title: "Local Resilience Forum Report"
author: ""
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: simplex
    social: menu
runtime: shiny
---

```{r setup, include=FALSE}
#### Do  Data pre processing stuff here ####

r = getOption("repos")
r["CRAN"] = "http://cran.r-project.org"
options(repos = r)

library(flexdashboard)
library(OpenStreetMap)
library(sf)
library(ggplot2)
library(tmap)
library(GISTools)
library(leaflet)
library(shiny)
library(datasets)
library(genalg)
library(scales)
library(tidyverse)
library(DT)

## Get the score data
# MSOA level
MSOAscores <- read.csv(paste(getwd(),"/data/FinalReportData/msoaScores_revised.csv",sep=""),na = "null")
# LA level
LAscores <- read.csv(paste(getwd(),"/data/FinalReportData/LAscores_revised.csv",sep=""),na = "null")
# LRF level
LRFscores <- read.csv(paste(getwd(),"/data/FinalReportData/LRFscores_revised.csv",sep=""),na = "null")
# Region level
Regionscores <- read.csv(paste(getwd(),"/data/FinalReportData/Regionscores_revised.csv",sep=""),na = "null")

# Get the MSOA shape files:
msoa_boundaries <- 
  read_sf(paste(getwd(),"/data/shapefiles/MSOAboundaries/MSOA_simplified_boundaries.shp", sep = ""))

# Join the regions on to the boundaries
# Get the lookup
RegionLookup <- read.csv(paste(getwd(),"/data/shapefiles/RegionLookup/Local_Authority_District_to_Region_December_2017_Lookup_in_England_.csv",sep=""),na = "null")

# Join the score data on
msoa_boundaries_scores <-
  msoa_boundaries %>% 
    left_join(MSOAscores[,c("msoa11cd","ladcd","ladnm","lrfcd","lrfnm","PopulationDensity_km2_score","Pct70_79_score","Pct80plus_score","EW_IMD_Decile_score","bph_score","RiskScore")], 
              by = c("msoa11cd"="msoa11cd")) %>% 
    rename(MSOA_PopulationDensity_km2_score = PopulationDensity_km2_score, 
           MSOA_Pct70_79_score = Pct70_79_score,
           MSOA_Pct80plus_score = Pct80plus_score,
           MSOA_EW_IMD_Decile_score = EW_IMD_Decile_score, 
           MSOA_bph_score = bph_score,
           MSOA_RiskScore = RiskScore) %>% 
    left_join(LAscores[,c("ladcd","PopulationDensity_km2_score","Pct70_79_score","Pct80plus_score","EW_IMD_Decile_score","bph_score","RiskScore")], 
            by = c("ladcd"="ladcd")) %>% 
     rename(LA_PopulationDensity_km2_score = PopulationDensity_km2_score, 
           LA_Pct70_79_score = Pct70_79_score,
           LA_Pct80plus_score = Pct80plus_score,
           LA_EW_IMD_Decile_score = EW_IMD_Decile_score, 
           LA_bph_score = bph_score,
           LA_RiskScore = RiskScore) %>% 
     left_join(LRFscores[,c("lrfcd","PopulationDensity_km2_score","Pct70_79_score","Pct80plus_score","EW_IMD_Decile_score","bph_score","RiskScore")], 
            by = c("lrfcd"="lrfcd")) %>% 
     rename(LRF_PopulationDensity_km2_score = PopulationDensity_km2_score, 
           LRF_Pct70_79_score = Pct70_79_score,
           LRF_Pct80plus_score = Pct80plus_score,
           LRF_EW_IMD_Decile_score = EW_IMD_Decile_score, 
           LRF_bph_score = bph_score,
           LRF_RiskScore = RiskScore) %>% 
    left_join(RegionLookup, by=c("ladcd"="LAD17CD")) %>% 
          mutate(RGN17NM = ifelse(str_detect(msoa11cd,"^W"),"Wales",as.character(RGN17NM))) %>% 
    left_join(Regionscores[,c("RGN17NM","PopulationDensity_km2_score","Pct70_79_score","Pct80plus_score","EW_IMD_Decile_score","bph_score","RiskScore")], 
            by = c("RGN17NM"="RGN17NM")) %>% 
     rename(Region_PopulationDensity_km2_score = PopulationDensity_km2_score, 
           Region_Pct70_79_score = Pct70_79_score,
           Region_Pct80plus_score = Pct80plus_score,
           Region_EW_IMD_Decile_score = EW_IMD_Decile_score, 
           Region_bph_score = bph_score,
           Region_RiskScore = RiskScore)

# Join the region on to the MSOA scores
MSOAscores<-
MSOAscores %>% 
  left_join(msoa_boundaries_scores[,c("msoa11cd","RGN17NM")] %>%
        st_set_geometry(.,NULL), by = c("msoa11cd"="msoa11cd")) %>% 
  distinct()

# transform to WGS84
msoa_boundaries_scores = st_transform(msoa_boundaries_scores, 4326)
```


Inputs {.sidebar}
===================================== 
```{r}
# add selectors 

# 1. Regions
# selectedRegion
regions = sort(unique(msoa_boundaries_scores$RGN17NM)) # Input the data.
# selectedLRF
selectInput("region_choice", label = h5('Select Region (first select "--" LRF)'),
            choices = regions, selected = "")

# selectedLRF
lrf_regions = sort(unique(levels(msoa_boundaries_scores$lrfnm))) # Input the data.
lrf_regions = c("--", lrf_regions)
selectInput("lrf_region_choice", label = h5("Select LRF (will override Region)"),
            choices = lrf_regions, selected = "--")


# 2. Indicators
indicators_lut = data.frame(
  facs = c("MSOA_PopulationDensity_km2_score",  "MSOA_Pct70_79_score",  "MSOA_Pct80plus_score",
            "MSOA_EW_IMD_Decile_score",  "MSOA_bph_score"),
  titles = c("Population Density", "70-79 Agegroup", "80+ Agegroup","Deprivation", 
             "Hospital Provision")) 

selectInput("indicator_choice", label = h5("Select Indicator (secondary map)"),
            choices = indicators_lut$titles, selected = "Population Density")

# return paramters for use in other places 
# **KEY POINT** in shiny apps = variables only exist in their code block 
# unless you make them reactive and pass them out as below
params_for_map <- reactive({
  region_choice = input$region_choice
  lrf_region_choice = input$lrf_region_choice
  indicator_choice = input$indicator_choice
  return(list(region_choice = region_choice, lrf_region_choice = lrf_region_choice, indicator_choice = indicator_choice))
})
```

***

**Information**

This dashboard shows the spatial distribution of aggregate COVID19 **risk** derived from **indicators** describing Population Density, older populations (the 70-79 and 80+ age groups), deprivation and hospital provision. This can either be shown at Region or Local Resilience Forum geographies.

How to use this dashboard:

1. **Select** a geography
2. **Select** an indicator

Selecting a geography will update all panels.
Slecting an indicator will update the panels focusing on a single indicator.

*NB: To select a region, the LRF option should be set to "--".*

***


Overview
===================================== 

### `r renderText(if(params_for_map()$lrf_region_choice == "--"){paste("Region details: ",params_for_map()$region_choice,sep="")}else{paste("Local Resilience Forum details: ",params_for_map()$lrf_region_choice,sep="")})`


Row 
-----------------------------------------------------------------------

### Risk score by MSOA

```{r}
# create map output - note all the work need to go within this function data mainoulations etc
# OR be passed to it 
# notice the first line the requires the outputs from the user inputs
# these are then assigned to internal variables and used for selecting etc
output$map1 <- renderLeaflet({
  # get parameters - region
    if(params_for_map()$lrf_region_choice == "--"){
    # Map the region

    # get parameters - region
    req(params_for_map())
    region_choice = params_for_map()$region_choice
    #lrf_region_choice = "West Yorkshire"
    # get local MSOAs
    this_region_msoas = msoa_boundaries_scores %>% filter(RGN17NM == region_choice)
    # get dissolved lrf_regions
    this_regions = msoa_boundaries_scores %>% filter(RGN17NM == region_choice) %>% 
    group_by(lrfnm) %>% 
    summarize(arse = sum(objectid, na.rm = TRUE))
        
  }
  else{
    # Map the LRF
  
    # get parameters - lrf_region
    req(params_for_map())
    lrf_region_choice = params_for_map()$lrf_region_choice
    #lrf_region_choice = "West Yorkshire"
    # get local MSOAs
    this_region_msoas = msoa_boundaries_scores %>% filter(lrfnm == lrf_region_choice)
    # get dissolved lrf_regions
    this_regions = msoa_boundaries_scores %>% filter(lrfnm == lrf_region_choice) %>% 
    group_by(ladnm) %>% 
    summarize(arse = sum(objectid, na.rm = TRUE))
    
  }

  # create an ordered factor palette 
  region.vals = this_region_msoas$MSOA_RiskScore
  cat.var <- character(length(region.vals))
  cat.var[region.vals >= 0 & region.vals <= 10] <- "1-10" 
  cat.var[region.vals > 10 & region.vals <= 20] <- "11-20" 
  cat.var[region.vals > 20 & region.vals <= 30] <- "21-30" 
  cat.var[region.vals > 30 & region.vals <= 40] <- "31-40"
  cat.var[region.vals > 40 & region.vals <= 50] <- "41-50" 
  region.vals <- cat.var
  pal <- colorFactor(
    #palette = (brewer.pal(5, "RdYlBu")[c(1,3,2,4,5)]),
    palette = c("#2C7BB6", "#ABD9E9", "#FFFFBF", "#FDAE61", "#D7191C"),
    #palette = c("#D7191C", "#FDAE61", "#FFFFBF", "#ABD9E9", "#2C7BB6"),
    domain = factor(c("1-10", "11-20", "21-30","31-40", "41-50")), 
    ordered = T)
  vals <- factor(c("1-10", "11-20", "21-30","31-40", "41-50"))
  # old palette for numeric variables - not as crisp
  #region.vals = region_msoas$MSOA_RiskScore
  #pal <- colorNumeric(
  #  #palette = (brewer.pal(5, "RdYlBu")[c(1,3,2,4,5)]),
  #  palette = c("#D7191C", "#FDAE61", "#FFFFBF", "#ABD9E9", "#2C7BB6"),
  #  domain = c(1,11,21,31,41,51), reverse =F)
  
  # create the map
  map1 <- leaflet(this_region_msoas) %>% 
    addTiles() %>%
    addProviderTiles(providers$OpenStreetMap) %>% 
    addPolygons(data = this_region_msoas,
                stroke = T, 
                weight = 1,
                smoothFactor = 0.5,
                fillOpacity = 0.7,
                opacity = 0.5, 
                fillColor = ~pal(region.vals)) %>%
    addPolygons(data=this_regions, stroke = T, weight = 2, fill = F, color = "black") %>%
    addLegend(pal = pal, values = region.vals,
            title = paste("Risk Score"), position = "bottomleft")  
  return(map1)

})
# call map
leafletOutput('map1', width = "100%", height = 600)  

```

### Indicator scores by MSOA (secondary map)

```{r}
# create map output - note all the work need to go within this function data mainoulations etc
# OR be passed to it 
# notice the first line the requires the outputs from the user inputs
# these are then assigned to internal variables and used for selecting etc
output$map2 <- renderLeaflet({

    if(params_for_map()$lrf_region_choice == "--"){
    # Map the region
    req(params_for_map())
    this_region_choice = params_for_map()$region_choice
    #this_region_choice = "Yorkshire and The Humber" 
    
    # get local MSOAs
    region_msoas = msoa_boundaries_scores %>% filter(RGN17NM == this_region_choice)
    # get dissolved regions
    regions = msoa_boundaries_scores %>% filter(RGN17NM == this_region_choice) %>% 
    group_by(lrfnm) %>% 
    summarize(arse = sum(objectid, na.rm = TRUE))
  }
  else{
  # get parameters - region
    req(params_for_map())
    this_region_choice = params_for_map()$lrf_region_choice
    #region_choice = "West Yorkshire" 
    
    # get local MSOAs
    region_msoas = msoa_boundaries_scores %>% filter(lrfnm == this_region_choice)
    # get dissolved regions
    regions = msoa_boundaries_scores %>% filter(lrfnm == this_region_choice) %>% 
    group_by(ladnm) %>% 
    summarize(arse = sum(objectid, na.rm = TRUE))
  }
  
  indicator_choice = params_for_map()$indicator_choice
  # development
  #indicator_choice = "Population Density"
  
  # link indicators nice drop-down names to field names in the data 
  indicators_lut = data.frame(
    facs = c("MSOA_PopulationDensity_km2_score",  "MSOA_Pct70_79_score",  "MSOA_Pct80plus_score",
            "MSOA_EW_IMD_Decile_score",  "MSOA_bph_score"),
    titles = c("Population Density", "70-79 Agegroup", "80+ Agegroup","Deprivation", 
             "Hospital Provision")) 
  indicator_var = as.character(
    indicators_lut$facs[match(indicator_choice, indicators_lut$titles)])

  # create an ordered factor palette 
  region.vals = as.vector(unlist(st_drop_geometry(region_msoas[, indicator_var])))
  cat.var <- character(length(region.vals))
  cat.var[region.vals >= 1 & region.vals <= 2] <- "1-2" 
  cat.var[region.vals >= 3 & region.vals <= 4] <- "3-4" 
  cat.var[region.vals >= 5 & region.vals <= 6] <- "5-6" 
  cat.var[region.vals >= 7 & region.vals <= 8] <- "7-8"
  cat.var[region.vals >= 9 & region.vals <= 10] <- "9-10" 
  region.vals <- cat.var
  pal <- colorFactor(
    palette = c("#2C7BB6", "#ABD9E9", "#FFFFBF", "#FDAE61", "#D7191C"),
    domain = factor(c("1-2", "3-4", "5-6","7-8", "9-10")), 
    ordered = T)
  
  # create the map
  map2 <- leaflet(region_msoas) %>% 
    
    addTiles() %>%
    addProviderTiles(providers$OpenStreetMap) %>% 
    addPolygons(data = region_msoas,
                stroke = T, 
                weight = 1,
                smoothFactor = 0.5,
                fillOpacity = 0.7,
                opacity = 0.5, 
                fillColor = ~pal(region.vals)) %>%
    addPolygons(data=regions, stroke = T, weight = 2, fill = F, color = "black") %>%
    addLegend(pal = pal, values = region.vals,
            title = paste(indicator_choice, " score",sep=""), position = "bottomleft")  
  return(map2)


})

# call map
leafletOutput('map2', width = "100%", height = 600)  


```

Row 
-----------------------------------------------------------------------

### **Overall Risk**

```{r}

renderGauge({

  if(params_for_map()$lrf_region_choice == "--"){
      # get parameters - region
      req(params_for_map())
      region_choice = params_for_map()$region_choice
      # get population density score
      this_risk_score = Regionscores %>%
                                 filter(RGN17NM == region_choice) %>%
                                 select(RiskScore) %>%
                                 pull()
  }
  else{
      # get parameters - region
      req(params_for_map())
      lrf_region_choice = params_for_map()$lrf_region_choice
      # get population density score
      this_risk_score = LRFscores %>%
                                 filter(lrfnm == lrf_region_choice) %>%
                                 select(RiskScore) %>%
                                 pull()    
  }
  
  gauge(this_risk_score, min = 0, max = 50, gaugeSectors(success = c(0, 15),warning=c(16,35),danger =c(36,50),
                                         colors=c("#2C7BB6","#FFFFBF","#D7191C")))
  
})

```

### Population Density

```{r}

renderGauge({

  if(params_for_map()$lrf_region_choice == "--"){
      # get parameters - region
      req(params_for_map())
      region_choice = params_for_map()$region_choice
      # get population density score
      this_population_density = Regionscores %>%
                                 filter(RGN17NM == region_choice) %>%
                                 select(PopulationDensity_km2_score) %>%
                                 pull()
  }
  else{
      # get parameters - region
      req(params_for_map())
      lrf_region_choice = params_for_map()$lrf_region_choice
      # get population density score
      this_population_density = LRFscores %>%
                                 filter(lrfnm == lrf_region_choice) %>%
                                 select(PopulationDensity_km2_score) %>%
                                 pull()    
  }
  
  gauge(this_population_density, min = 0, max = 10, gaugeSectors(success = c(0, 3),warning=c(4,7),danger =c(8,10),
                                         colors=c("#2C7BB6","#FFFFBF","#D7191C")))
  
})

```


### Aged 70-79

```{r}

renderGauge({

  if(params_for_map()$lrf_region_choice == "--"){
      # get parameters - region
      req(params_for_map())
      region_choice = params_for_map()$region_choice
      # get population density score
      this_7079 = Regionscores %>%
                                 filter(RGN17NM == region_choice) %>%
                                 select(Pct70_79_score) %>%
                                 pull()
  }
  else{
      # get parameters - region
      req(params_for_map())
      lrf_region_choice = params_for_map()$lrf_region_choice
      # get population density score
      this_7079 = LRFscores %>%
                                 filter(lrfnm == lrf_region_choice) %>%
                                 select(Pct70_79_score) %>%
                                 pull()    
  }
  
  gauge(this_7079, min = 0, max = 10, gaugeSectors(success = c(0, 3),warning=c(4,7),danger =c(8,10),
                                         colors=c("#2C7BB6","#FFFFBF","#D7191C")))
  
})

```

### Aged 80+

```{r}

renderGauge({

  if(params_for_map()$lrf_region_choice == "--"){
      # get parameters - region
      req(params_for_map())
      region_choice = params_for_map()$region_choice
      # get population density score
      this_80plus = Regionscores %>%
                                 filter(RGN17NM == region_choice) %>%
                                 select(Pct80plus_score) %>%
                                 pull()
  }
  else{
      # get parameters - region
      req(params_for_map())
      lrf_region_choice = params_for_map()$lrf_region_choice
      # get population density score
      this_80plus = LRFscores %>%
                                 filter(lrfnm == lrf_region_choice) %>%
                                 select(Pct80plus_score) %>%
                                 pull()    
  }
  
  gauge(this_80plus, min = 0, max = 10, gaugeSectors(success = c(0, 3),warning=c(4,7),danger =c(8,10),
                                         colors=c("#2C7BB6","#FFFFBF","#D7191C")))
  
})

```



### Deprivation

```{r}

renderGauge({

  if(params_for_map()$lrf_region_choice == "--"){
      # get parameters - region
      req(params_for_map())
      region_choice = params_for_map()$region_choice
      # get population density score
      this_deprivation = Regionscores %>%
                                 filter(RGN17NM == region_choice) %>%
                                 select(EW_IMD_Decile_score) %>%
                                 pull()
  }
  else{
      # get parameters - region
      req(params_for_map())
      lrf_region_choice = params_for_map()$lrf_region_choice
      # get population density score
      this_deprivation = LRFscores %>%
                                 filter(lrfnm == lrf_region_choice) %>%
                                 select(EW_IMD_Decile_score) %>%
                                 pull()    
  }
  
  gauge(this_deprivation, min = 0, max = 10, gaugeSectors(success = c(0, 3),warning=c(4,7),danger =c(8,10),
                                         colors=c("#2C7BB6","#FFFFBF","#D7191C")))
  
})

```


### Hospital provision

```{r}

renderGauge({

  if(params_for_map()$lrf_region_choice == "--"){
      # get parameters - region
      req(params_for_map())
      region_choice = params_for_map()$region_choice
      # get population density score
      this_hospital_provision = Regionscores %>%
                                 filter(RGN17NM == region_choice) %>%
                                 select(bph_score) %>%
                                 pull()
  }
  else{
      # get parameters - region
      req(params_for_map())
      lrf_region_choice = params_for_map()$lrf_region_choice
      # get population density score
      this_hospital_provision = LRFscores %>%
                                 filter(lrfnm == lrf_region_choice) %>%
                                 select(bph_score) %>%
                                 pull()    
  }
  
  gauge(this_hospital_provision, min = 0, max = 10, gaugeSectors(success = c(0, 3),warning=c(4,7),danger =c(8,10),
                                         colors=c("#2C7BB6","#FFFFBF","#D7191C")))
  
})

```



Row 
-----------------------------------------------------------------------

### Comparison with national picture

```{r}
# specify what is going on here! 
plotOutput("distPlot")

# create a renderplot
# again note the passing of  paramters 
# there is some duplicartion going on here - the filtering could be done once for example! 
output$distPlot <- renderPlot({

  if(params_for_map()$lrf_region_choice == "--"){
  this_region_choice = params_for_map()$region_choice
  #lrf_region_choice = "West Yorkshire"
  # Get the LRF Risk Scores
  this_RiskScores <-  MSOAscores %>% filter(RGN17NM == this_region_choice) %>% dplyr::select(RiskScore)
  }
  else{
    this_region_choice = params_for_map()$lrf_region_choice
    #lrf_region_choice = "West Yorkshire"
    # Get the LRF Risk Scores
    this_RiskScores <-  MSOAscores %>% filter(lrfnm == this_region_choice) %>% dplyr::select(RiskScore)
  }

  # Get the LRF Risk Scores
  LRFRiskScores <-  MSOAscores %>% filter(lrfnm == this_region_choice) %>% dplyr::select(RiskScore)
  # Merge the datasets
  RiskScores <- 
    data.frame(Type = "National", RiskScore = MSOAscores$RiskScore) %>%
    rbind(data.frame(Type = this_region_choice, RiskScore = this_RiskScores$RiskScore))
  ggplot(data = RiskScores, aes(x=RiskScore, fill=Type)) +
  geom_density(alpha=.5) +
  labs(title = "Distribution of Risk Scores") +
  labs(y="Density") +
  labs(x="Risk Scores")+
  theme(text = element_text(size=10), legend.position="bottom", legend.box = "horizontal")
  # add any additional ggplot parameters  

})

```

### `r renderText(if(params_for_map()$lrf_region_choice == "--"){paste("Rankings of Local Resilience Forums in  ",params_for_map()$region_choice,sep="")}else{paste("Rankings of Local Authorities in ",params_for_map()$lrf_region_choice,sep="")})`

```{r}

renderDT({

  if(params_for_map()$lrf_region_choice == "--"){
      # get parameters - region
      req(params_for_map())
      region_choice = params_for_map()$region_choice
      # get data for table
      LRFscores %>%
          filter(RGN17NM == region_choice) %>%
          arrange(RiskScore) %>%
          select("LRF" = lrfnm,
                 "Overall Risk" = RiskScore,
                 "Population Density" = PopulationDensity_km2_score,
                 "70-79 Agegroup" = Pct70_79_score,
                 "80+ Agegroup" = Pct80plus_score,
                 "Deprivation" = EW_IMD_Decile_score,
                 "Hospital Provision" = bph_score) -> tmp2

      brks1 <- seq(10,49,10)
      brks2 <- seq(2, 9, 2)
  }
  else{
      # get parameters - region
      req(params_for_map())
      lrf_region_choice = params_for_map()$lrf_region_choice
      # get population density score
      LAscores %>%
        filter(lrfnm == lrf_region_choice) %>%
        arrange(RiskScore) %>%
        select("Local Authority" = ladnm,
               "Overall Risk" = RiskScore,
               "Population Density" = PopulationDensity_km2_score,
               "70-79 Agegroup" = Pct70_79_score,
               "80+ Agegroup" = Pct80plus_score,
               "Deprivation" = EW_IMD_Decile_score,
               "Hospital Provision" = bph_score) -> tmp2

        brks1 <- seq(10,49,10)
        brks2 <- seq(2, 9, 2)
  }

  clrs <- c("#95bcd9","#d4eaf2","#fefddd","#fcd5ad","#e88987")

  font.size <- "6pt"

  # ## uses a bit of css - from here 
  # # https://stackoverflow.com/questions/44101055/changing-font-size-in-r-datatables-dt
  # tmp2 %>% 
  #    DT::datatable(
  #      options=list(
  #        initComplete = htmlwidgets::JS(
  #           "function(settings, json) {",
  #           paste0("$(this.api().table().container()).css({'font-size': '", font.size, "'});"),
  #           "}"), autoWidth = TRUE, pageLength = 5, scrollX = T,
  #               columnDefs = list(list(width = '10%', className = 'dt-center', targets = c(2:7)))
  #        ) 
  #      ) %>% 
  #     formatStyle(names(tmp2[names(tmp2) != "Risk Score"]),backgroundColor = styleInterval(brks2, clrs),fontWeight = 'bold',color = 'black') %>% 
  #     formatStyle(names(tmp2[2]), backgroundColor = styleInterval(brks1, clrs),fontWeight = 'bold',color = 'black')
  
    tmp2 %>% DT::datatable(options=list(
    autoWidth = TRUE, scrollX = T,columnDefs = list(list(width = '15%', className = 'dt-center', targets = c(2:7))))) %>% 
    formatStyle(names(tmp2[!(names(tmp2) %in% c("Overall Risk"))]),backgroundColor = styleInterval(brks2, clrs), color = 'black',border = '1px solid #c4c4c4') %>% 
    formatStyle(names(tmp2[2]), backgroundColor = styleInterval(brks1, clrs), color = 'black',border = '1px solid #c4c4c4')
  
})


# below is some css code for manipulating the header for the multi-page panel FD

```

Benchmarks {data-orientation=rows}
===================================== 

### `r renderText(if(params_for_map()$lrf_region_choice == "--"){paste("Region summary: ",params_for_map()$region_choice,sep="")}else{paste("Local Resilience Forum summary: ",params_for_map()$lrf_region_choice,sep="")})`


Row
-------------------------------------

### **Overall Risk**

```{r}

renderGauge({

  if(params_for_map()$lrf_region_choice == "--"){
      # get parameters - region
      req(params_for_map())
      region_choice = params_for_map()$region_choice
      # get population density score
      this_risk_score = Regionscores %>%
                                 filter(RGN17NM == region_choice) %>%
                                 select(RiskScore) %>%
                                 pull()
  }
  else{
      # get parameters - region
      req(params_for_map())
      lrf_region_choice = params_for_map()$lrf_region_choice
      # get population density score
      this_risk_score = LRFscores %>%
                                 filter(lrfnm == lrf_region_choice) %>%
                                 select(RiskScore) %>%
                                 pull()    
  }
  
  gauge(this_risk_score, min = 0, max = 50, gaugeSectors(success = c(0, 15),warning=c(16,35),danger =c(36,50),
                                         colors=c("#2C7BB6","#FFFFBF","#D7191C")))
  
})

```

### Population Density

```{r}

renderGauge({

  if(params_for_map()$lrf_region_choice == "--"){
      # get parameters - region
      req(params_for_map())
      region_choice = params_for_map()$region_choice
      # get population density score
      this_population_density = Regionscores %>%
                                 filter(RGN17NM == region_choice) %>%
                                 select(PopulationDensity_km2_score) %>%
                                 pull()
  }
  else{
      # get parameters - region
      req(params_for_map())
      lrf_region_choice = params_for_map()$lrf_region_choice
      # get population density score
      this_population_density = LRFscores %>%
                                 filter(lrfnm == lrf_region_choice) %>%
                                 select(PopulationDensity_km2_score) %>%
                                 pull()    
  }
  
  gauge(this_population_density, min = 0, max = 10, gaugeSectors(success = c(0, 3),warning=c(4,7),danger =c(8,10),
                                         colors=c("#2C7BB6","#FFFFBF","#D7191C")))
  
})

```


### Aged 70-79

```{r}

renderGauge({

  if(params_for_map()$lrf_region_choice == "--"){
      # get parameters - region
      req(params_for_map())
      region_choice = params_for_map()$region_choice
      # get population density score
      this_7079 = Regionscores %>%
                                 filter(RGN17NM == region_choice) %>%
                                 select(Pct70_79_score) %>%
                                 pull()
  }
  else{
      # get parameters - region
      req(params_for_map())
      lrf_region_choice = params_for_map()$lrf_region_choice
      # get population density score
      this_7079 = LRFscores %>%
                                 filter(lrfnm == lrf_region_choice) %>%
                                 select(Pct70_79_score) %>%
                                 pull()    
  }
  
  gauge(this_7079, min = 0, max = 10, gaugeSectors(success = c(0, 3),warning=c(4,7),danger =c(8,10),
                                         colors=c("#2C7BB6","#FFFFBF","#D7191C")))
  
})

```

### Aged 80+

```{r}

renderGauge({

  if(params_for_map()$lrf_region_choice == "--"){
      # get parameters - region
      req(params_for_map())
      region_choice = params_for_map()$region_choice
      # get population density score
      this_80plus = Regionscores %>%
                                 filter(RGN17NM == region_choice) %>%
                                 select(Pct80plus_score) %>%
                                 pull()
  }
  else{
      # get parameters - region
      req(params_for_map())
      lrf_region_choice = params_for_map()$lrf_region_choice
      # get population density score
      this_80plus = LRFscores %>%
                                 filter(lrfnm == lrf_region_choice) %>%
                                 select(Pct80plus_score) %>%
                                 pull()    
  }
  
  gauge(this_80plus, min = 0, max = 10, gaugeSectors(success = c(0, 3),warning=c(4,7),danger =c(8,10),
                                         colors=c("#2C7BB6","#FFFFBF","#D7191C")))
  
})

```



### Deprivation

```{r}

renderGauge({

  if(params_for_map()$lrf_region_choice == "--"){
      # get parameters - region
      req(params_for_map())
      region_choice = params_for_map()$region_choice
      # get population density score
      this_deprivation = Regionscores %>%
                                 filter(RGN17NM == region_choice) %>%
                                 select(EW_IMD_Decile_score) %>%
                                 pull()
  }
  else{
      # get parameters - region
      req(params_for_map())
      lrf_region_choice = params_for_map()$lrf_region_choice
      # get population density score
      this_deprivation = LRFscores %>%
                                 filter(lrfnm == lrf_region_choice) %>%
                                 select(EW_IMD_Decile_score) %>%
                                 pull()    
  }
  
  gauge(this_deprivation, min = 0, max = 10, gaugeSectors(success = c(0, 3),warning=c(4,7),danger =c(8,10),
                                         colors=c("#2C7BB6","#FFFFBF","#D7191C")))
  
})

```


### Hospital provision

```{r}

renderGauge({

  if(params_for_map()$lrf_region_choice == "--"){
      # get parameters - region
      req(params_for_map())
      region_choice = params_for_map()$region_choice
      # get population density score
      this_hospital_provision = Regionscores %>%
                                 filter(RGN17NM == region_choice) %>%
                                 select(bph_score) %>%
                                 pull()
  }
  else{
      # get parameters - region
      req(params_for_map())
      lrf_region_choice = params_for_map()$lrf_region_choice
      # get population density score
      this_hospital_provision = LRFscores %>%
                                 filter(lrfnm == lrf_region_choice) %>%
                                 select(bph_score) %>%
                                 pull()    
  }
  
  gauge(this_hospital_provision, min = 0, max = 10, gaugeSectors(success = c(0, 3),warning=c(4,7),danger =c(8,10),
                                         colors=c("#2C7BB6","#FFFFBF","#D7191C")))
  
})

```


Row 
-------------------------------------

### **Ranking table**

```{r}
# straightforwatd with DT::datatable

renderDT({

  if(params_for_map()$lrf_region_choice == "--"){
      # get parameters - region
      req(params_for_map())
      region_choice = params_for_map()$region_choice
      # get data for table
      Regionscores %>% 
          arrange(RiskScore) %>% 
          select("Region" = RGN17NM, 
                 "Risk Score" = RiskScore,
                 "Population Density Score" = PopulationDensity_km2_score,
                 "70-79 Agegroup Score" = Pct70_79_score,
                 "80+ Agegroup Score" = Pct80plus_score,
                 "Deprivation Score" = EW_IMD_Decile_score,
                 "Hospital Provision Score" = bph_score) -> tmp
  
      brks1 <- seq(10,49,10)
      brks2 <- seq(2, 9, 2)

  }
  else{
      # get parameters - region
      req(params_for_map())
      lrf_region_choice = params_for_map()$lrf_region_choice
      # get population density score
      LRFscores %>% 
                arrange(RiskScore) %>% 
                select("Local Resilience Forum" = lrfnm, 
                       "Risk Score" = RiskScore,
                       "Population Density Score" = PopulationDensity_km2_score,
                       "70-79 Agegroup Score" = Pct70_79_score,
                       "80+ Agegroup Score" = Pct80plus_score,
                       "Deprivation Score" = EW_IMD_Decile_score,
                       "Hospital Provision Score" = bph_score) -> tmp
        
        brks1 <- seq(10,49,10)
        brks2 <- seq(2, 9, 2)
  }

  clrs <- c("#95bcd9","#d4eaf2","#fefddd","#fcd5ad","#e88987")

  tmp %>% DT::datatable(options=list(
    autoWidth = TRUE, scrollX = T,columnDefs = list(list(width = '12%', className = 'dt-center', targets = c(2:7))))) %>% 
    formatStyle(names(tmp[names(tmp) != "Overall Risk"]),backgroundColor = styleInterval(brks2, clrs), color = 'black',border = '1px solid #c4c4c4') %>% 
    formatStyle(names(tmp[2]), backgroundColor = styleInterval(brks1, clrs), color = 'black')
  
})

# below is some css code for manipulating the header for the multi-page panel FD

```



 <style>

    .storyboard-nav .sbframelist {
        margin: 0 auto;
        width: 94%;
        height: 50px;
        overflow: hidden;
        text-shadow: none;
        margin-bottom: 8px;
    }

    .storyboard-nav .sbnext, .storyboard-nav .sbprev {
        float: left;
        width: 2%;
        height: 50px;
        font-size: 50px;
    }

    </style>
